Time Series Modeling of Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-09-05 Ben_Manuscripts/stochastic_transport/Outline.tex
Some reorganization and more methods

  % MRS1: I would start with something more central to the content of the paper - how do solutes move in complex separations membranes?  Let people know right from the start what the paper is about.  This paragraph should still be in the intro, but start with something that captures the main question of the paper. 
  % BJC2: This paragraph will need more tweaking but is the gist of what I'm thinking
  Mathematical descriptions of transport in complex separations membranes are a powerful 
  way to understand mechanisms and formulate membrane design principles.
  \begin{itemize}
    \item The complexity of a model generally parallels the complexity of the 
    transport mechanism at hand, as well as the desired outputs.
    \item In dense homogeneous membranes, the solution-diffusion model can extract
    diffusion and partition coefficients and has successfully predicted solute transport
    rates.
    \item Analogously, pore-flow models yield predictions of diffusion coefficients
    and solute transport rates in nanoporous membranes.~\cite{wijmans_solution-diffusion_1995}
    \item Single particle tracking allows us to further characterize more complex
    diffusive behavior.
    \item Finally, Molecular simulation provides a framework for studying both single
    particle dynamics and bulk transport properties with atomic resolution.
    \item All of these approaches facilitate speculation on the molecular origins of
    separations and suggest experiments that should be run by attempting to give a more
    intuitive understanding of how solutes move as a function of their environment.
%    \item The hydrodynamic Ferry model is the simplest pore-flow model, with extensions such
%    as the Donnan-Steric Pore Model which includes extra terms for the pressure gradient
%    across the membrane and membrane charge.
%    \item Dischinger et al. created an empirical correlation to determine the
%    effect of solute physicochemical properties on solute rejection.
  \end{itemize}

@@

  % BJC1: tie this paragraph into above by commenting that highly selective membranes
  % often have complex mechanistic reasons that aren't explained by simpler models
  We need highly selective membranes in order to perform efficient separations. \\

@@

  We can only learn so much from experiment. MD can give us mechanistic insights with
  atomistic resolution so that we can intelligently design new membranes for 
  solute-specific separations.\\

@@

  Unfortunately, the timescales that we can simulate with MD are insufficient to be
  able to make well-converged predictions of macroscopic transport properties 
  traditionally used to characterize membranes in the lab. \\
  \begin{itemize}
    \item However, if we use descriptive stochastic models that sufficiently capture solute
    dynamics, then we could project long timescale behavior in addition to gaining
    a deeper understanding of solute behavior on short timescales.
  \end{itemize}

@@

  \noindent We can use the observations of transport from our previous work in order to create 
  state-based models.
  \begin{itemize}
  	\item We know that dynamics differ between solutes moving inside the pores and 
  	in the tails.
  	\item We can use the anomalous diffusion approach to model our data as a 
  	function of radial distance from the closest pore center.
  	\item Alternatively, we can abandon the anomalous diffusion theory and adapt the 
  	methods of Markov state modeling.
  \end{itemize}

@@

  In this work we attempt to model the long timescale behavior of the four 
  fastest moving solutes studied in our previous work.
  \begin{itemize}
    \item Specifically, we study methanol, urea, ethylene glycol and acetic acid
    \item In addition to moving quickly, these solutes have a range of chemical
    functionality and experience each of the three trapping mechanisms to different
    degrees.
    \item It is our goal to reproduce the MSDs exhibited by each solute on MD timescales
    and then to project the long-term dynamics of each solute. 
    \item We explore two modeling approaches
%  	\item The third uses an infinite hidden Markov model (iHMM), an unsupervised machine
%  	learning algorithm which groups solute behavior into different dynamical states.
  	% BJC: somewhere emphasize that this last approach is powerful since it doesn't 
  	% require anything different in systems with more complex geometries (i.e. QI)
  \end{itemize}

@@

  We ran all MD simulations and energy minimizations using GROMACS 2018. We  % needs gromacs citations
  performed all post-simulation trajectory using python scripts which are available
  %MRS: eventually want to say what scripts were used to do what, but that is not at the outline stage!
  %BJC1: I usually put a table like that in the SI. Is that sufficient?
  online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.

@@

@@

  % BJC: Should this be in the results? Lots of figures to show in support of the claims below
  % MRS: can you provide mechanistic reasoning for the below? Then can show the claims for the reasonable possibilities.
  % BJC1: modified this paragraph to parallel the flow chart. I'm still not sure the
  % best place for this. It seems like it belongs in the discussion, but I need to 
  % justify the choice in model so I can write the methods about the chosen models
  \noindent We believe that solutes in the system studied here exhibit subordinated 
  fractional Brownian motion (sFBM) where the parent process is FBM and the 
  leading process is a CTRW. 
  \begin{itemize}
    \item Working down the flow chart...
  	\item We observe non-stationary $z$-coordinate traces of each solute's
  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
  	\item Combined with the observation that the ensemble-averaged MSD differs
  	from the time-averaged MSD, we have evidence of non-ergodicity in this system, 
  	a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}  % BJC: need a figure to show this
% BJC1: following two points are weak. Linearity of CTRW doesn't necessarily hold up on short time scales.
%  	\item For a pure CTRW, the time-averaged MSD should be linear.
%  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
%  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
%  	information), which suggests that there is another underlying subdiffusive mechanism.
	\item The process is likely subordinated to another process because the hop 
	lengths recorded after each dwell period are anti-correlated.
    % BJC1: need to eliminate RWF. I think a geometric argument should be convincing enough. Our
    % system doesn't have a fractal-like structure. Monomer positions fluctuate enough that
    % solutes can access any part of the membrane over time.
  	\item Given the viscoelastic nature of the monomers in our system, we believe
  	the hop lengths can be modeled with FBM. 
  	% BJC1 : probably won't need this equation. It's really just to validate my sfbm
  	% simulation procedure. Could go in supporting information with a plot showing that
  	% my sims fit to t^alpha*beta
 	\item For subordinated FBM, it can be shown that
  	\begin{equation}
  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
  	\end{equation}
  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
  \end{itemize}

@@

  \noindent The distribution of dwell times is expected to fit a power law
  distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  \begin{itemize}
	\item Because we are limited to taking measurements at discrete values
	dictated by the output frequency of our simulation trajectories, we fit the
	empirical dwell times to a discrete power law distribution whose maximum
	likelihood $\alpha$ parameter we calculated by maximizing the following
	likelihood function: 
        \begin{equation}
	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
	\beta\sum_{i=1}^{n} \text{ln}~x_i 
	\label{eqn:powerlaw_likelihood}
	\end{equation}
	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
	where $x_{min}$ is the smallest measured value of
	$x_i$.~\cite{clauset_power-law_2009} 
	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
        %MRS1: can just say bootstrapping.
  \end{itemize}

  \noindent FBM processes can be described using the Hurst parameter, $H$, where 
  $H = \beta/2$.
  \begin{itemize}
  	\item Brownian motion is recovered for $H = 0.5$
	\item The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
    \begin{equation}
	\gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
	\label{eqn:autocovariance}
	\end{equation}
	where $k$ is the number of increments between hops.
	\item We obtained H by performing a least squares fit of Equation~\ref{eqn:autocovariance}
	to the empirically measured autocovariance function.
	\item We used statistical bootstrapping to generate a distribution of $H$ 
	values. %BJC: can provide more detail in supporting or just reference python script
  \end{itemize}

  In general, we observe different dynamical behavior when solutes move inside the
  pore versus in the tail region.
  %MRS: could present the two models sequentiually.  Talk about one COULD have multiple modes, then in results present 1, then 2. 
  \begin{itemize}
    \item This inspired two models of varying complexity.
    \item We created a simple, single mode model with a single $\alpha$, $\sigma$ and $H$
    parameter fit to each solute.
    \item Our second, two mode model assigns a set of parameters to each of 2 modes based
    on the solute's radial location.
    \item Solutes in mode 1 are in the pore region defined as less than 0.75 nm from any
    pore center and all else are in mode 2, the tail region. 
    \item We determined this cut-off and described how we calculated radial 
    distance from the pore center in our previous work~\cite{coscia_chemically_2019}
  \end{itemize}

  For the two mode model, we needed to define a probability transition matrix 
  describing transitions between the tail and pore region.

@@

%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
%  magnitude longer than our molecular simulations.
  \noindent For each solute, we simulated 10000 5 $\mu$s sFBM trajectories. 
  \begin{itemize}
	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
	distributions.
	\item We propagated each trajectory until the total time equaled or exceeded 5 $\mu$s, 
	then truncated the last data point so that the total time exactly equaled 5 $\mu$s. 
    \item Valid comparisons are only possible between fixed length sFBM simulations. The
    power law dwell time behavior gives rise to the aging phenomenon, embodied by
    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
    \item We reported the MSD after 5 $\mu$s with corresponding 95 \% intervals
% Following probably better suited for supporting information, if included at all
%	\item We randomly sample Gaussian hop lengths using the
%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
%	\item We randomly sampled dwell times from a discrete power law
%	distribution based on the recommendations of Clauset et
%	al.~\cite{clauset_power-law_2009}: 
%	\begin{equation}
%	x = \lfloor
%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
%	\label{eqn:discrete_powerlaw_draws}
%	\end{equation}
%	where $r$ is randomly drawn from a uniform distribution which we simulated
%	with \texttt{numpy.random.uniform}.
%	\item We found that thermal noise does not significantly influence the MSD and
%	therefore did not add any noise to the simulated trajectories. (See supporting info)
  \end{itemize}

@@

  \noindent We recorded the $z$-direction displacement at each time step in order to construct
  individual emission distributions for each state and transition between states.
  \begin{itemize}
    \item This is where we have modified the standard MSM framework.
    \item While the dynamics of the states themselves are important, the 
    majority of observations involve transitions between states, so properly modeling
    the transition dynamics is even more important.
    \item This results in 64 distinct emission distributions. Some are far more
    populated than others. % BJC1: need to look into lumping transition emissions into one distribution
    %\item The shape of the distributions are symmetric and heavy-tailed. 
  \end{itemize}

  % BJC2: An abbreviated from of this paragraph probably belongs in previous section
  % since I'll be using subordinated levy motion.
  \noindent We modeled the emission distributions as L\'evy stable distributions.  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
  \begin{itemize}
    \item For independent and identically distributed (iid) random variables, the 
    generalized central limit theorem guarantees convergence of the associated 
    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
    % BJC: ``For sums of independent, iid random variables with proper normalization to the
%    sample size, the generalized central limit theorem guarantees the convergence of
%    the associated PDF to a L\'evy stable PDF even though the variance of these random
%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
    \item The characteristic equation describing the Fourier transform of a L\'evy 
    stable PDF is given below:
    \begin{equation}
    p_{\alpha, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
    \end{equation}
    \item Where $\omega$ is defined with something that is complicated to format and can be 
    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
    functions, is the Gaussian PDF ($\alpha$ = 2).
    \item The more general family of L\'evy stable distributions allows
    greater flexibility in defining the observed emission distribution PDFs.
    \item In the case that the empirical emission distributions are iid, sequential draws
    from a L\'evy stable PDF defines a L\'evy process. 
    \item We can relax the iid assumption and maintain the flexibility of L\'evy stable 
    probability distributions if we instead consider the dynamics to be governed by a
    non-Gaussian Ornstein-Uhlenbeck (OU) process.\cite{barndorffnielsen_non-gaussian_2001} % BJC: replaces Wiener process with Levy process
    %MRS1: you many consider putting some of the long explanations in supporrting. 
    \item OU processes contain temporal dependence but the marginal observation distributions
    are consistent with the underlying stochastic driver.~\cite{taufer_simulation_2009}
    \item We will discuss the implications of each.  
    % MRS: does the process described above include the motion within the state? That is something I feel that the
    %standard MSM doesn't include either, since they are typically interested just in the distribution of states in equilibrium, not the diffusion. 
    % BJC1: Right, I added a sentence to the paragraph before this one to make it clear that we
    % are adding to the standard MSM.
  \end{itemize}

@@

  We simulated realizations of the stochastic process using the probability transition
  matrix and emission distributions.
  \begin{itemize}
    \item For each trajectory simulated, we chose an initial state randomly from a 
    uniform distribution. %BJC: could construct initial distribution but I'm not sure how reliable that is based on 24 solutes that are started in the pore center.
    \item We randomly drew subsequent state transitions and corresponding emissions 
    from the rows of the probability transition matrix and the appropriate emission
    distribution respectively.
  \end{itemize}

@@

  \subsection{Subordinated Fractional Brownian Motion Modeling}\label{section:sFBM}

  Using the techniques from Section~\ref{method:model_sFBM}, we extracted values 
  of $\sigma$, $\alpha$, $H$ and $\lambda$ for each solute for the 1 and 2 mode models 
  (see Table~\ref{table:sfbm_params}).
  \begin{itemize}
    \item In most cases, it is easy to relate the values of $\sigma$, $\alpha$ 
    and $H$ presented in Table~\ref{table:sfbm_params} to the simulated MSD values. 
  	\item Higher values of $\sigma$ indicate larger average hop lengths.
  	\item Higher values of $\alpha$ mean that there will be less sampling of 
  	long dwell times.
  	\item Higher values of $\lambda$ truncates the power law distribution earlier
  	preventing extremely long dwell times.
  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
  	of anti-correlation.
  	\item All of which contribute to an overall increase in the MSD.
  \end{itemize}

@@

  \noindent The choice between Levy and Gaussian distributions has only a small effect, 
  but the Levy appears to fit emission distributions better.

@@

  \subsection{Markov State Model Fits}\label{section:msm_results}
  % BJC2: This section should parallel the previous section in terms of presentation of results.

>>>>

  % MRS1: I would start with something more central to the content of the paper - how do solutes move in complex separations membranes?  Let people know right from the start what the paper is about.  This paragraph should still be in the intro, but start with something that captures the main question of the paper. 
  % BJC2: This paragraph will need more tweaking but is the gist of what I'm thinking
  % BJC2: I'm not sure if this is exactly what you meant though
%  Making sense of solute motion in complex separations membranes is central to 
%  understanding transport mechanisms and formulating membrane design principles.
  Mathematical descriptions of transport in complex separations membranes are a powerful 
  way to understand mechanisms and formulate membrane design principles.
  \begin{itemize}
    \item The complexity of a model generally parallels the complexity of the 
    transport mechanism at hand, as well as the desired outputs.
    \item In dense homogeneous membranes, the solution-diffusion model can extract
    diffusion and partition coefficients and has successfully predicted solute transport
    rates.
    \item Analogously, pore-flow models yield predictions of diffusion coefficients
    and solute transport rates in nanoporous membranes.~\cite{wijmans_solution-diffusion_1995}
    \item Single particle tracking allows us to further characterize more complex
    diffusive behavior.
    \item Finally, Molecular simulation provides a framework for studying both single
    particle dynamics and bulk transport properties with atomic resolution.
    \item All of these approaches facilitate speculation on the molecular origins of
    separations and suggest experiments that should be run by attempting to give a more
    intuitive understanding of how solutes move as a function of their environment.
%    \item The hydrodynamic Ferry model is the simplest pore-flow model, with extensions such
%    as the Donnan-Steric Pore Model which includes extra terms for the pressure gradient
%    across the membrane and membrane charge.
%    \item Dischinger et al. created an empirical correlation to determine the
%    effect of solute physicochemical properties on solute rejection.
  \end{itemize}

@@

  % BJC1: tie this paragraph into above by commenting that highly selective membranes
  % often have complex mechanistic reasons that aren't explained by simpler models
  These approaches can be especially useful for designing highly selective membranes. \\
  %BJC2: this paragraph will contain examples of highly selective separations

@@

  We can only learn so much from experiment. MD can give us mechanistic insights with
  atomistic resolution so that we can intelligently design new membranes for 
  solute-specific separations.\\
  %BJC2: simple models from first paragraph fail to adequately describe transport.

@@

  Unfortunately, the timescales that we can simulate with MD are insufficient to be
  able to make well-converged predictions of macroscopic transport properties 
  traditionally used to characterize membranes in the lab.
  \begin{itemize}
    \item However, if we use descriptive stochastic models that sufficiently capture solute
    dynamics, then we could project long timescale behavior in addition to gaining
    a deeper understanding of solute behavior on short timescales.
  \end{itemize}

@@

%  \noindent We can use the observations of transport from our previous work in order to create 
%  state-based models.
%  \begin{itemize}
%  	\item We know that dynamics differ between solutes moving inside the pores and 
%  	in the tails.
%  	\item We can use the anomalous diffusion approach to model our data as a 
%  	function of radial distance from the closest pore center.
%  	\item Alternatively, we can abandon the anomalous diffusion theory and adapt the 
%  	methods of Markov state modeling.
%  \end{itemize}

@@

  In this work we apply the two modeling approaches in order to predict the long
  timescale behavior of the four fastest moving solutes studied in our previous work.
  \begin{itemize}
    \item Specifically, we study methanol, urea, ethylene glycol and acetic acid
    \item In addition to moving quickly, these solutes have a range of chemical
    functionality and experience each of the three trapping mechanisms to different
    degrees.
    \item It is our goal to reproduce the MSDs exhibited by each solute on MD timescales
    and then to project the long-term dynamics of each solute. 
%  	\item The third uses an infinite hidden Markov model (iHMM), an unsupervised machine
%  	learning algorithm which groups solute behavior into different dynamical states.
  	% BJC: somewhere emphasize that this last approach is powerful since it doesn't 
  	% require anything different in systems with more complex geometries (i.e. QI)
  \end{itemize}

@@

  We ran all MD simulations and energy minimizations using GROMACS 2018. We  % needs gromacs citations
  performed all post-simulation trajectory analysis using python scripts which are available
  %MRS: eventually want to say what scripts were used to do what, but that is not at the outline stage!
  %BJC1: I usually put a table like that in the SI. Is that sufficient?
  online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.

@@

  We determined equilibration based on the solute partition between the pore and tail
  region.

@@

  % BJC: Should this be in the results? Lots of figures to show in support of the claims below
  % MRS: can you provide mechanistic reasoning for the below? Then can show the claims for the reasonable possibilities.
  % BJC1: modified this paragraph to parallel the flow chart. I'm still not sure the
  % best place for this. It seems like it belongs in the discussion, but I need to 
  % justify the choice in model so I can write the methods about the chosen models
  % BJC2: Perhaps just say that we think it's sFBM and move the proof to discussion.
  \noindent We believe that solutes in the system studied here exhibit subordinated 
  fractional Brownian motion (sFBM) where the parent process is FBM and the 
  leading process is a CTRW. 
  \begin{itemize}
    \item Working down the flow chart...
  	\item We observe non-stationary $z$-coordinate traces of each solute's
  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
  	\item Combined with the observation that the ensemble-averaged MSD differs
  	from the time-averaged MSD, we have evidence of non-ergodicity in this system, 
  	a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}  % BJC: need a figure to show this
% BJC1: following two points are weak. Linearity of CTRW doesn't necessarily hold up on short time scales.
%  	\item For a pure CTRW, the time-averaged MSD should be linear.
%  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
%  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
%  	information), which suggests that there is another underlying subdiffusive mechanism.
	\item The process is likely subordinated to another process because the hop 
	lengths recorded after each dwell period are anti-correlated.
    % BJC1: need to eliminate RWF. I think a geometric argument should be convincing enough. Our
    % system doesn't have a fractal-like structure. Monomer positions fluctuate enough that
    % solutes can access any part of the membrane over time.
  	\item Given the viscoelastic nature of the monomers in our system, we believe
  	the hop lengths can be modeled with FBM. 
  	% BJC1 : probably won't need this equation. It's really just to validate my sfbm
  	% simulation procedure. Could go in supporting information with a plot showing that
  	% my sims fit to t^alpha*beta
 	\item For subordinated FBM, it can be shown that
  	\begin{equation}
  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
  	\end{equation}
  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
  \end{itemize}

@@

  \noindent The distribution of dwell times is expected to fit a power law
  distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  \begin{itemize}
	\item Because we are limited to taking measurements at discrete values
	dictated by the output frequency of our simulation trajectories, we fit the
	empirical dwell times to a discrete power law distribution whose maximum
	likelihood $\alpha$ parameter we calculated by maximizing the following
	likelihood function: 
    \begin{equation}
	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
	\beta\sum_{i=1}^{n} \text{ln}~x_i 
	\label{eqn:powerlaw_likelihood}
	\end{equation}
	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
	where $x_{min}$ is the smallest measured value of
	$x_i$.~\cite{clauset_power-law_2009} 
	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
	$\alpha$ using bootstrapping.\cite{efron_introduction_1994} 
  \end{itemize}

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. 
  \begin{itemize}
    \item We can not observe dwell times longer than the length of a single trajectory.
    \item In fact the longest dwell time observed by solutes in this study is X.
    \item In order to compare our anomalous diffusion model to MD results we need to 
    bound the dwell time distribution.
    \item We do this by adding an exponential cut-off to the power law so the dwell 
    time distribution is of the form:
    \begin{equation}
    t^{-1 - \alpha}e^{-\lambda t}
    \end{equation}
    \item We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
    \begin{equation}
    \mathcal{L}(\alpha, \lambda) = n*(1 - \alpha)ln\lambda - n*ln\Gamma(1 - \alpha, x_{min}\lambda) - \alpha\sum_{i=1}^{n}ln x_i - \lambda\sum_{i=1}^n x_i
    \end{equation}
  \end{itemize}

  \noindent FBM processes can be described using the Hurst parameter, $H$.
  \begin{itemize}
  	\item Brownian motion is recovered for $H = 0.5$
	\item The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
    \begin{equation}
	\gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
	\label{eqn:autocovariance}
	\end{equation}
	where $k$ is the number of increments between hops.
	\item We obtained H by performing a least squares fit of Equation~\ref{eqn:autocovariance}
	to the empirically measured autocovariance function.
	\item We used statistical bootstrapping to generate a distribution of $H$ 
	values. %BJC: can provide more detail in supporting or just reference python script
	\item There are more complicated ways to calculate H but well-converged estimates 
	require far more data than we have access to.
  \end{itemize}

  \noindent If the distribution of hops is not Gaussian, we can model them with the
  more general class of L\'evy stable distributions.
  \begin{itemize}
    \item For independent and identically distributed (iid) random variables, the 
    generalized central limit theorem guarantees convergence of the associated 
    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
    % BJC: ``For sums of independent, iid random variables with proper normalization to the
%    sample size, the generalized central limit theorem guarantees the convergence of
%    the associated PDF to a L\'evy stable PDF even though the variance of these random
%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
    \item The characteristic equation describing the Fourier transform of a L\'evy 
    stable PDF is given below:
    \begin{equation}
    p_{\alpha, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
    \end{equation}
    \item Where $\omega$ is defined with something that is complicated to format and can be 
    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
    functions, is the Gaussian PDF ($\alpha$ = 2).
    \item We assume symmetric distributions centered about 0 implying that $\beta$ and $\mu$ are both 0.
  \end{itemize}

  \noindent If the hops are correlated, we can describe their motion as subordinated 
  fractional L\'evy motion.
  \begin{itemize}
    \item The hurst parameter can again be used to describe the degree of anitcorrelation.
    \item It has the form: %BJC2: need to see if there is an analytical form for H
    %BJC2: might need to use a different way to estimate H (which is more standard): https://pypi.org/project/hurst/
  \end{itemize}

  In general, we observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region.
  %MRS: could present the two models sequentiually.  Talk about one COULD have multiple modes, then in results present 1, then 2. 
  \begin{itemize}
    \item This inspired two models of varying complexity.
    \item We created a simple, single mode model with a single $\alpha$, $\sigma$ and $H$
    parameter fit to each solute.
    \item Our second, two mode model assigns a set of parameters to each of 2 modes based
    on the solute's radial location.
    \item Solutes in mode 1 are in the pore region defined as less than 0.75 nm from any
    pore center and all else are in mode 2, the tail region. 
    \item We determined this cut-off and described how we calculated radial 
    distance from the pore center in our previous work~\cite{coscia_chemically_2019}
  \end{itemize}

  For the two mode model, we needed to define a probability transition matrix 
  describing transitions between the tail and pore region. \\

@@

%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
%  magnitude longer than our molecular simulations.
  \noindent For each solute, we simulated 10000 5 $\mu$s sFBM trajectories. 
  \begin{itemize}
	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
	distributions.
	\item We use the python package \texttt{fbm} to simulate fractional Brownian motion and 
	our own implementation of the algorithm by Stoev and Taqqu to simulation fraction L\'evy motion.~\cite{stoev_simulation_2004}
	\item We propagated each trajectory until the total time equaled or exceeded 5 $\mu$s, 
	then truncated the last data point so that the total time exactly equaled 5 $\mu$s. 
    \item Valid comparisons are only possible between fixed length sFBM simulations. The
    power law dwell time behavior gives rise to the aging phenomenon, embodied by
    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
    \item We reported the time-averaged MSD after 2 $\mu$s time lags with corresponding 
    95 \% intervals
% Following probably better suited for supporting information, if included at all
%	\item We randomly sample Gaussian hop lengths using the
%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
%	\item We randomly sampled dwell times from a discrete power law
%	distribution based on the recommendations of Clauset et
%	al.~\cite{clauset_power-law_2009}: 
%	\begin{equation}
%	x = \lfloor
%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
%	\label{eqn:discrete_powerlaw_draws}
%	\end{equation}
%	where $r$ is randomly drawn from a uniform distribution which we simulated
%	with \texttt{numpy.random.uniform}.
%	\item We found that thermal noise does not significantly influence the MSD and
%	therefore did not add any noise to the simulated trajectories. (See supporting info)
  \end{itemize}

@@

  \noindent We recorded the $z$-direction displacement at each time step in order to construct
  individual emission distributions for each state and transition between states.
  \begin{itemize}
    \item This is where we have modified the standard MSM framework.
    \item While the dynamics of the states themselves are important, the 
    majority of observations involve transitions between states, so properly modeling
    the transition dynamics is even more important.
    \item This results in 64 distinct emission distributions. Some are far more
    populated than others. % BJC1: need to look into lumping transition emissions into one distribution
    \item We modeled the emission distributions as L\'evy stable distributions. 
    %\item The shape of the distributions are symmetric and heavy-tailed. 
  \end{itemize}

  % BJC2: Moved the meat of this paragraph to previous section
  % since I'll be using subordinated levy motion.
  \noindent  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
%  \begin{itemize}
%    \item For independent and identically distributed (iid) random variables, the 
%    generalized central limit theorem guarantees convergence of the associated 
%    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
%    % BJC: ``For sums of independent, iid random variables with proper normalization to the
%%    sample size, the generalized central limit theorem guarantees the convergence of
%%    the associated PDF to a L\'evy stable PDF even though the variance of these random
%%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
%    \item The characteristic equation describing the Fourier transform of a L\'evy 
%    stable PDF is given below:
%    \begin{equation}
%    p_{\alpha, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
%    \end{equation}
%    \item Where $\omega$ is defined with something that is complicated to format and can be 
%    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
%    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
%    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
%    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
%    functions, is the Gaussian PDF ($\alpha$ = 2).
%    \item The more general family of L\'evy stable distributions allows
%    greater flexibility in defining the observed emission distribution PDFs.
%    \item In the case that the empirical emission distributions are iid, sequential draws
%    from a L\'evy stable PDF defines a L\'evy process. 
%    \item We can relax the iid assumption and maintain the flexibility of L\'evy stable 
%    probability distributions if we instead consider the dynamics to be governed by a
%    non-Gaussian Ornstein-Uhlenbeck (OU) process.\cite{barndorffnielsen_non-gaussian_2001} % BJC: replaces Wiener process with Levy process
%    %MRS1: you many consider putting some of the long explanations in supporrting. 
%    \item OU processes contain temporal dependence but the marginal observation distributions
%    are consistent with the underlying stochastic driver.~\cite{taufer_simulation_2009}
%    \item We will discuss the implications of each.  
%    % MRS: does the process described above include the motion within the state? That is something I feel that the
%    %standard MSM doesn't include either, since they are typically interested just in the distribution of states in equilibrium, not the diffusion. 
%    % BJC1: Right, I added a sentence to the paragraph before this one to make it clear that we
%    % are adding to the standard MSM.
%  \end{itemize}

@@

  We simulated realizations of the stochastic process using the probability transition
  matrix and emission distributions.
  \begin{itemize}
    \item For each trajectory simulated, we chose an initial state randomly from a 
    uniform distribution. %BJC: could construct initial distribution but I'm not sure how reliable that is based on 24 solutes that are started in the pore center.
    \item We randomly drew subsequent state transitions and corresponding emissions 
    from the rows of the probability transition matrix and the appropriate emission
    distribution respectively.
    \item We added correlation between transitions as well as correlation to sequences
    of emissions while dwelling in specific states.
  \end{itemize}

@@

  \subsection{Anomlaous Diffusion Modeling}\label{section:sFBM}

  %BJC2: I think it makes sense to show the data supporting that this is likely
  % sFBM here in the discussion. The methods would just point here.
  We determined that transport is likely governed by sFBM using the flow chart in
  Figure X.
  \begin{itemize}
    \item Show weak ergodicity breaking, non-stationarity and correlation between hops
    \item Geometric argument against random walk on fractal?
  \end{itemize}

  Using the techniques from Section~\ref{method:model_sFBM}, we extracted values 
  of $\sigma$, $\alpha$, $H$ and $\lambda$ for each solute for the 1 and 2 mode models 
  (see Table~\ref{table:sfbm_params}).
  \begin{itemize}
    \item In most cases, it is easy to relate the parameter values 
    Table~\ref{table:sfbm_params} to the simulated MSD values. 
  	\item Higher values of $\sigma$ indicate larger average hop lengths.
  	\item Higher values of $\alpha$ mean that there will be less sampling of 
  	long dwell times.
  	\item Higher values of $\lambda$ truncate the power law distribution earlier
  	preventing extremely long dwell times.
  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
  	of anti-correlation.
  	\item All of which contribute to an overall increase in the MSD.
  \end{itemize}

@@

  \noindent The choice between Levy and Gaussian distributions has only a small effect, 
  but the Levy appears to fit emission distributions better. \\

@@

  \subsection{Markov State Modeling}\label{section:msm_results}
  % BJC2: This section should parallel the previous section in terms of presentation of results.
